Kindly Bent to Free Us

### 2019-07-04 kindly/lang.tex
Add a section explaining typing of bindings and closures.

\subsubsection{Bindings and Weakening}

@@

\begin{figure}
  \centering
  \begin{subfigure}{0.4\linewidth}
    \begin{mathpar}
      \ruleSDRegion
    \end{mathpar}
    \caption{The {\sc Region} rule}
  \end{subfigure}\hfill
  \begin{subfigure}{0.6\linewidth}
    \centering
    \begin{tabular}
      {@{}>{$}r<{$}@{ $\Lleftarrow$ }
      >{$}c<{$}@{ $\rightsquigarrow_n^{x}$ }
      >{$}l<{$}
      r}

@@

@@

\begin{figure}
  \centering
  \begin{subfigure}{0.35\linewidth}
    \begin{mathpar}
      \ruleSDPair
    \end{mathpar}
    \caption{The {\sc Pair} rule}
  \end{subfigure}\hfill
  \begin{subfigure}{0.6\linewidth}
    \centering
    \begin{tabular}
      {@{}>{$}r<{$}@{ $\Lleftarrow$ }
      >{$}c<{$}@{ $=$ }
      >{$}c<{$}@{ $\ltimes$ }
      >{$}c<{$}r}

>>>>

We now present the essential parts of our \lang's type system. A complete
description of the system is available in \cref{appendix:sdtyping}.
In this section, we focus on chosen parts of our system
through a set of selected rules.
%
We first define the following typing, kinding and constraint judgements:
\begin{description}
\item[$\inferS{C}{\E}{e}{\tau}$ --]
  Expression $e$ has type $\tau$ in environment $\E$ under constraints $C$.
\item[$\inferSK{C}{\E}{\tau}{k}$ --]
  Type $\tau$ has kind $k$ in environment $\E$ under constraints $C$.
\item[$\entail{D}{C}$ --] Constraint $D$ implies constraint $C$.
\end{description}

We will now present the novel aspects of our system which are necessary to handle
three specific features: binders, borrows, and sharing.

@@

\begin{figure}[!h]
  \centering
  \begin{subfigure}{0.4\linewidth}
    \begin{mathpar}
      \ruleSDRegion
    \end{mathpar}
    \caption{The {\sc Region} rule}
  \end{subfigure}\hfill
  \begin{subfigure}{0.6\linewidth}
    \centering
    \begin{tabular}
      {@{}>{$}r<{$}@{ $\Lleftarrow$ }
      >{$}c<{$}@{ $\rightsquigarrow_n^{x}$ }
      >{$}l<{$}
      r}

@@

\subsubsection{Bindings and Closures}

One essential aspect of linear types is to control which variables
are allowed to be unused. This is usually done through \emph{weakening},
which allow to discard bindings from the environment.
Another important feature is to control \emph{captures} done by closures.
In \lang, we enforce both properties through the use of environment-wide
kind inequalities, which we note $\Cleq{\E}{k}$.
The intuitive meaning of $\Cleq{\E}{k}$ is that for all bindings
$\bvar{x}{\tau}$ in $\E$,
if type $\tau$ has kind $k'$ ($\inferSK{C}{\E}{\tau}{k'}$)
then $\Cleq{k'}{k}$.
While this definition is incomplete, it is sufficient to understand
its use in the {\sc Abs} and {\sc Var} rules shown in \cref{selectrules:binders}.
%
The {\sc Var} rule looks up the type scheme of the variable $x$ in
the environment $\E$
and instantiate a concrete type through the substitution $\unif$. It then
checks that the other bindings in $\E$ can safely be discarded by
ensuring they are not linear. This is achieved through the constraint
$\Cleq{\E\Sdel{X}}{\kaff_\infty}$.
%
The {\sc Lam} constraints must ensures that if the body of the lambda captures
linear or affine variable, the content will be reflected in the kind
annotated on the arrow, such as $\tau_2 \tarr{k} \tau_1$.
In order to do so, we constraint all the bindings of $\E$ to be less than $k$.
If one of the binding of $\E$ constraints a type whose kind is affine,
we will derive the constraints $\Cleq{\kaff_n}{k}$, which ensures that
the kind on the arrow is at least affine.

\begin{figure}[!h]
  \centering
  \begin{mathpar}
    \ruleSDLam

    \ruleSDVar
  \end{mathpar}
  \caption{The {\sc Lam} and {\sc Var} rules}
  \label{selectrules:binders}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \begin{subfigure}{0.35\linewidth}
    \begin{mathpar}
      \ruleSDPair
    \end{mathpar}
    \caption{The {\sc Pair} rule}
  \end{subfigure}\hfill
  \begin{subfigure}{0.6\linewidth}
    \centering
    \begin{tabular}
      {@{}>{$}r<{$}@{ $\Lleftarrow$ }
      >{$}c<{$}@{ $=$ }
      >{$}c<{$}@{ $\ltimes$ }
      >{$}c<{$}r}
